Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-08-14 analysis/Study1.qmd
EGA| colours data 1-3

rez_hclust <- make_hclust(data1af)
rez_ega <- make_ega(data1af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data1af, n = 3, cols = c("F1" = colors[["Burp"]], "F2" = colors[["Urinate"]], 
                                            "F3" = colors[["Bruise"]]))
rez_cfa1a  <- make_cfa(data1af)

@@

rez_hclust <- make_hclust(data1b)
rez_ega <- make_ega(data1b, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data1b, n = 4, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]], 
                                            "F3" = colors[["Sneeze"]], "F4" = colors[["Wind"]]))

@@

rez_hclust <- make_hclust(data1bf)
rez_ega <- make_ega(data1af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data1bf, n = 3, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]], 
                                            "F3" = colors[["Cough"]], "F4" = colors[["Itch"]]))
rez_cfa1b  <- make_cfa(data1bf)

@@

rez_hclust <- make_hclust(data2)
rez_ega <- make_ega(data2, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data2, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Bruise"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Sex arousal"]]))

@@

rez_hclust <- make_hclust(data2f)
rez_ega <- make_ega(data2f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data2f, n = 3, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Bruise"]], 
                                            "F3" = colors[["Hungry"]]))
rez_cfa2  <- make_cfa(data2f)

@@

rez_hclust <- make_hclust(data3)
rez_ega <- make_ega(data3, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data3, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Urinate"]], 
                                            "F3" = colors[["Blood Sugar"]], "F4" = colors[["Sex arousal"]]))

@@

rez_hclust <- make_hclust(data3f)
rez_ega <- make_ega(data3f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data3f, n = 3, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Hungry"]], 
                                            "F3" = colors[["Blood Sugar"]]))
rez_cfa3  <- make_cfa(data3f)

@@

rez_hclust <- make_hclust(data12f)
rez_ega <- make_ega(data12f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data12f, n = 5, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Burp"]], 
                                             "F3" = colors[["Heart"]], "F4" = colors[["Pain"]], "F5" = colors[["Sneeze"]]))
# rez_cfa12  <- make_cfa(data12f)

>>>>

rez_hclust <- make_hclust(data1af)
rez_ega <- make_ega(data1af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data1af, n = 3, cols = c("F1"  colors[["Burp"]], "F2" = colors[["Urinate"]], 
                                            "F3" = colors[["Bruise"]]))
rez_cfa1a  <- make_cfa(data1af)

@@

rez_hclust <- make_hclust(data1b)
rez_ega <- make_ega(data1b, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Defecate"]], "C3" = colors[["Bruise"]], "C4" = colors[["Sneeze"]], 
  "C5" = colors[["Wind"]], "C6" = colors[["Temp"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data1b, n = 4, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]], 
                                            "F3" = colors[["Sneeze"]], "F4" = colors[["Wind"]]))

@@

rez_hclust <- make_hclust(data1bf)
rez_ega <- make_ega(data1af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data1bf, n = 3, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]], 
                                            "F3" = colors[["Cough"]], "F4" = colors[["Itch"]]))
rez_cfa1b  <- make_cfa(data1bf)

@@

rez_hclust <- make_hclust(data2)
rez_ega <- make_ega(data2, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Urinate"]], "C4" = colors[["Sneeze"]], 
  "C5" = colors[["Pain"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data2, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Bruise"]], 
                                            "F3" = colors[["Heart"]], "F4" = colors[["Sex arousal"]]))

@@

rez_hclust <- make_hclust(data2f)
rez_ega <- make_ega(data2f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
  "C5" = colors[["Wind"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data2f, n = 3, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Bruise"]], 
                                            "F3" = colors[["Hungry"]]))
rez_cfa2  <- make_cfa(data2f)

@@

rez_hclust <- make_hclust(data3)
rez_ega <- make_ega(data3, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Urinate"]], "C3" = colors[["Pain"]], "C4" = colors[["Sneeze"]], 
  "C5" = colors[["Wind"]], "C6" = colors[["Bruise"]], "C7" = colors[["Muscles"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data3, n = 4, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Urinate"]], 
                                            "F3" = colors[["Blood Sugar"]], "F4" = colors[["Sex arousal"]]))

@@

rez_hclust <- make_hclust(data3f)
rez_ega <- make_ega(data3f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Urinate"]], "C3" = colors[["Sneeze"]], "C4" = colors[["Wind"]], 
  "C5" = colors[["Pain"]], "C6" = colors[["Bruise"]], "C7" = colors[["Muscles"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data3f, n = 3, cols = c("F1" = colors[["Cough"]], "F2" = colors[["Hungry"]], 
                                            "F3" = colors[["Blood Sugar"]]))
rez_cfa3  <- make_cfa(data3f)

@@

rez_hclust <- make_hclust(data12f)
rez_ega <- make_ega(data8af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data12f, n = 5, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Burp"]], 
                                             "F3" = colors[["Heart"]], "F4" = colors[["Pain"]], "F5" = colors[["Sneeze"]]))
# rez_cfa12  <- make_cfa(data12f)
